### 2023-10-25 main.tex
^^
ll
l
kk

Using \eqref{bosonicKX} we rewrite the term of \eqref{siteHadamardII} with Lie generator $E_{Na}^{x}$ on the right hand side of \eqref{siteHadamardII} as 

@@

>>>>

Using the above equation we rewrite the right hand side term of \eqref{siteHadamardII} with Lie generator $E_{Na}^{x}$ as 

@@

\Psi^{''}(\tau_1,\ldots,\tau_L)&=\left[\prod_{x=1}^{L}\lambda_{\tau_{x}}^{\delta_{\tau_x<N}}\right] \frac{\Gamma\left(2+L-\sum_{x=1}^{L}\delta_{\tau_{x}<N}\right)}{\Gamma\left(2+L\right)}\prod_{x=1}^{L} \frac{\Gamma\left(2+L-x-\sum_{j=x+1}^{L}\delta_{\tau_{j}<N}\right)}{\Gamma\left(2+L-x-\sum_{j=x}^{L}\delta_{\tau_{j}<N}\right)}\\
&=\left[\prod_{x=1}^{L}\lambda_{\tau_{x}}^{\delta_{\tau_x<N}}\right] \frac{\Gamma\left(2 \right)}{\Gamma\left(2+L\right)}\prod_{x=1}^{L} \frac{\Gamma\left(3+L-x-\sum_{j=x}^{L}\delta_{\tau_{x}<N}\right)}{\Gamma\left(2+L-x-\sum_{j=x}^{L}\delta_{\tau_{x}<N}\right)}\\
&=\left[\prod_{x=1}^{L}\lambda_{\tau_{x}}^{\delta_{\tau_x<N}}\right] \frac{\Gamma\left(2 \right)}{\Gamma\left(2+L\right)}\prod_{x=1}^{L} \frac{\Gamma\left(3+\sum_{j=x}^{L}\delta_{\tau_{x},N}\right)}{\Gamma\left(2+\sum_{j=x}^{L}\delta_{\tau_{x},N}\right)}\\
&=\left[\prod_{x=1}^{L}\lambda_{\tau_{x}}^{\delta_{\tau_x<N}}\right] \frac{\Gamma\left(2 \right)}{\Gamma\left(2+L\right)}\prod_{x=1}^{L} \left(2+\sum_{j=x}^{L}\delta_{\tau_{x},N}\right)\\
% &=\left[\prod_{x=1}^{L}\lambda_{\tau_{x}}^{\delta_{\tau_x<N}}\right] \frac{\Gamma\left(2 \right)}{\Gamma\left(2+L\right)}\prod_{x=1}^{L}\frac{1}{\Gamma(-1)} B(3+L-x-\sum_{j=x}^{L}\delta_{\tau_{x}<N},-1)\\
Looks like there is a mistake somewhere...
